An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2021-09-23 latex_files/images/chapter4/mae2_hist_t1_romc_bo.tex
changed notation to be inline with ROMC paper
small changes

title={ROMC (Bayesian Optimisation) - Histogram of the parameter \(\displaystyle \theta_1\)},

@@

\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.315,1.59230812208571);
\draw[draw=none,fill=color0] (axis cs:0.315,0) rectangle (axis cs:0.33,2.04310565145056);
\draw[draw=none,fill=color0] (axis cs:0.33,0) rectangle (axis cs:0.345,2.19382815490065);
\draw[draw=none,fill=color0] (axis cs:0.345,0) rectangle (axis cs:0.36,2.20021699441589);
\draw[draw=none,fill=color0] (axis cs:0.36,0) rectangle (axis cs:0.375,2.51506116421806);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.39,2.44880980882892);
\draw[draw=none,fill=color0] (axis cs:0.39,0) rectangle (axis cs:0.405,2.65904829491329);
\draw[draw=none,fill=color0] (axis cs:0.405,0) rectangle (axis cs:0.42,2.73250343027527);
\draw[draw=none,fill=color0] (axis cs:0.42,0) rectangle (axis cs:0.435,2.82852250487442);
\draw[draw=none,fill=color0] (axis cs:0.435,0) rectangle (axis cs:0.45,2.82331312648089);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.465,2.90135211837164);
\draw[draw=none,fill=color0] (axis cs:0.465,0) rectangle (axis cs:0.48,2.88136478592358);
\draw[draw=none,fill=color0] (axis cs:0.48,0) rectangle (axis cs:0.495,2.53560317010369);
\draw[draw=none,fill=color0] (axis cs:0.495,0) rectangle (axis cs:0.51,2.3564598017404);
\draw[draw=none,fill=color0] (axis cs:0.51,0) rectangle (axis cs:0.525,2.22420707945385);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.54,2.33534256536061);
\draw[draw=none,fill=color0] (axis cs:0.54,0) rectangle (axis cs:0.555,2.00495652659749);
\draw[draw=none,fill=color0] (axis cs:0.555,0) rectangle (axis cs:0.57,1.74992091039568);
\draw[draw=none,fill=color0] (axis cs:0.57,0) rectangle (axis cs:0.585,1.83870977452066);
\draw[draw=none,fill=color0] (axis cs:0.585,0) rectangle (axis cs:0.6,1.6578788920657);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.615,1.55026416918985);
\draw[draw=none,fill=color0] (axis cs:0.615,0) rectangle (axis cs:0.63,1.62152961093496);
\draw[draw=none,fill=color0] (axis cs:0.63,0) rectangle (axis cs:0.645,1.6437730803435);
\draw[draw=none,fill=color0] (axis cs:0.645,0) rectangle (axis cs:0.66,1.66640493128548);
\draw[draw=none,fill=color0] (axis cs:0.66,0) rectangle (axis cs:0.675,1.32365272171391);
\draw[draw=none,fill=color0] (axis cs:0.675,0) rectangle (axis cs:0.69,1.14155317519524);
\draw[draw=none,fill=color0] (axis cs:0.69,0) rectangle (axis cs:0.705,1.17480604967746);
\draw[draw=none,fill=color0] (axis cs:0.705,0) rectangle (axis cs:0.72,1.20896637137188);
\draw[draw=none,fill=color0] (axis cs:0.72,0) rectangle (axis cs:0.735,1.26617555858479);
\draw[draw=none,fill=color0] (axis cs:0.735,0) rectangle (axis cs:0.75,1.10815016078187);
\draw[draw=none,fill=color0] (axis cs:0.75,0) rectangle (axis cs:0.765,1.01575133068398);
\draw[draw=none,fill=color0] (axis cs:0.765,0) rectangle (axis cs:0.78,0.778653581806476);
\draw[draw=none,fill=color0] (axis cs:0.78,0) rectangle (axis cs:0.795,0.658517776017212);
\draw[draw=none,fill=color0] (axis cs:0.795,0) rectangle (axis cs:0.81,0.522857721601219);
\draw[draw=none,fill=color0] (axis cs:0.81,0) rectangle (axis cs:0.825,0.649384569447495);
\draw[draw=none,fill=color0] (axis cs:0.825,0) rectangle (axis cs:0.84,0.571069158563703);
\draw[draw=none,fill=color0] (axis cs:0.84,0) rectangle (axis cs:0.855,0.362376122626364);
\draw[draw=none,fill=color0] (axis cs:0.855,0) rectangle (axis cs:0.87,0.275087556542002);
\draw[draw=none,fill=color0] (axis cs:0.87,0) rectangle (axis cs:0.885,0.255847252846728);
\draw[draw=none,fill=color0] (axis cs:0.885,0) rectangle (axis cs:0.9,0.406941618766892);
\draw[draw=none,fill=color0] (axis cs:0.9,0) rectangle (axis cs:0.915,0.192257669195406);
\draw[draw=none,fill=color0] (axis cs:0.915,0) rectangle (axis cs:0.93,0.204927790769102);
\draw[draw=none,fill=color0] (axis cs:0.93,0) rectangle (axis cs:0.945,0.203525138747285);
\draw[draw=none,fill=color0] (axis cs:0.945,0) rectangle (axis cs:0.96,0.113584712363094);
\draw[draw=none,fill=color0] (axis cs:0.96,0) rectangle (axis cs:0.975,0.0662010640185658);
\draw[draw=none,fill=color0] (axis cs:0.975,0) rectangle (axis cs:0.99,0.116253091726246);
\draw[draw=none,fill=color0] (axis cs:0.99,0) rectangle (axis cs:1.005,0.0456418048890116);

@@

0.502312841390367 0
0.502312841390367 3.5

@@

\addlegendentry{$\mu = 0.502$}

@@

0.294820390999603 1
0.660267860059204 1

@@

\addlegendentry{$\sigma = 0.166$}

>>>>

title={ROMC (BO) - \(\displaystyle \theta_1\)},

@@

\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.315,1.61050759359378);
\draw[draw=none,fill=color0] (axis cs:0.315,0) rectangle (axis cs:0.33,1.93197020366126);
\draw[draw=none,fill=color0] (axis cs:0.33,0) rectangle (axis cs:0.345,2.17257862381295);
\draw[draw=none,fill=color0] (axis cs:0.345,0) rectangle (axis cs:0.36,2.3025919446582);
\draw[draw=none,fill=color0] (axis cs:0.36,0) rectangle (axis cs:0.375,2.42910062383181);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.39,2.77208977160826);
\draw[draw=none,fill=color0] (axis cs:0.39,0) rectangle (axis cs:0.405,2.91890254170224);
\draw[draw=none,fill=color0] (axis cs:0.405,0) rectangle (axis cs:0.42,2.79720744902878);
\draw[draw=none,fill=color0] (axis cs:0.42,0) rectangle (axis cs:0.435,2.89385988809184);
\draw[draw=none,fill=color0] (axis cs:0.435,0) rectangle (axis cs:0.45,3.03707063266652);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.465,2.96625904171146);
\draw[draw=none,fill=color0] (axis cs:0.465,0) rectangle (axis cs:0.48,2.87224832339805);
\draw[draw=none,fill=color0] (axis cs:0.48,0) rectangle (axis cs:0.495,2.65419765058084);
\draw[draw=none,fill=color0] (axis cs:0.495,0) rectangle (axis cs:0.51,2.62169851287656);
\draw[draw=none,fill=color0] (axis cs:0.51,0) rectangle (axis cs:0.525,2.32485253886239);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.54,2.14150464429012);
\draw[draw=none,fill=color0] (axis cs:0.54,0) rectangle (axis cs:0.555,2.24693369229431);
\draw[draw=none,fill=color0] (axis cs:0.555,0) rectangle (axis cs:0.57,2.33863073514552);
\draw[draw=none,fill=color0] (axis cs:0.57,0) rectangle (axis cs:0.585,2.14663274237078);
\draw[draw=none,fill=color0] (axis cs:0.585,0) rectangle (axis cs:0.6,1.90924828657755);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.615,1.71866221248833);
\draw[draw=none,fill=color0] (axis cs:0.615,0) rectangle (axis cs:0.63,1.67767714633082);
\draw[draw=none,fill=color0] (axis cs:0.63,0) rectangle (axis cs:0.645,1.5285521718297);
\draw[draw=none,fill=color0] (axis cs:0.645,0) rectangle (axis cs:0.66,1.07857259816532);
\draw[draw=none,fill=color0] (axis cs:0.66,0) rectangle (axis cs:0.675,1.06467730589615);
\draw[draw=none,fill=color0] (axis cs:0.675,0) rectangle (axis cs:0.69,1.31604561147561);
\draw[draw=none,fill=color0] (axis cs:0.69,0) rectangle (axis cs:0.705,1.16959736883555);
\draw[draw=none,fill=color0] (axis cs:0.705,0) rectangle (axis cs:0.72,0.934947898685309);
\draw[draw=none,fill=color0] (axis cs:0.72,0) rectangle (axis cs:0.735,0.697393683133471);
\draw[draw=none,fill=color0] (axis cs:0.735,0) rectangle (axis cs:0.75,0.826583507333401);
\draw[draw=none,fill=color0] (axis cs:0.75,0) rectangle (axis cs:0.765,0.526592417514156);
\draw[draw=none,fill=color0] (axis cs:0.765,0) rectangle (axis cs:0.78,0.744305041869243);
\draw[draw=none,fill=color0] (axis cs:0.78,0) rectangle (axis cs:0.795,0.507002670950614);
\draw[draw=none,fill=color0] (axis cs:0.795,0) rectangle (axis cs:0.81,0.550468818640814);
\draw[draw=none,fill=color0] (axis cs:0.81,0) rectangle (axis cs:0.825,0.531452195144458);
\draw[draw=none,fill=color0] (axis cs:0.825,0) rectangle (axis cs:0.84,0.449213153956996);
\draw[draw=none,fill=color0] (axis cs:0.84,0) rectangle (axis cs:0.855,0.46212842931813);
\draw[draw=none,fill=color0] (axis cs:0.855,0) rectangle (axis cs:0.87,0.307647048984769);
\draw[draw=none,fill=color0] (axis cs:0.87,0) rectangle (axis cs:0.885,0.39272346125025);
\draw[draw=none,fill=color0] (axis cs:0.885,0) rectangle (axis cs:0.9,0.33527111008569);
\draw[draw=none,fill=color0] (axis cs:0.9,0) rectangle (axis cs:0.915,0.236505059054111);
\draw[draw=none,fill=color0] (axis cs:0.915,0) rectangle (axis cs:0.93,0.27054174354952);
\draw[draw=none,fill=color0] (axis cs:0.93,0) rectangle (axis cs:0.945,0.0792063139920926);
\draw[draw=none,fill=color0] (axis cs:0.945,0) rectangle (axis cs:0.96,0.0290615761452173);
\draw[draw=none,fill=color0] (axis cs:0.96,0) rectangle (axis cs:0.975,0.0742518004133052);
\draw[draw=none,fill=color0] (axis cs:0.975,0) rectangle (axis cs:0.99,0.037125900206652);
\draw[draw=none,fill=color0] (axis cs:0.99,0) rectangle (axis cs:1.005,0.0323749806537868);

@@

0.494409356161276 0
0.494409356161276 3.5

@@

\addlegendentry{$\mu = 0.494$}

@@

0.292577624981475 1
0.645122958573331 1

@@

\addlegendentry{$\sigma = 0.160$}

### 2021-09-23 latex_files/images/chapter4/mae2_hist_t2_romc.tex
changed notation to be inline with ROMC paper

\draw[draw=none,fill=color0] (axis cs:-0.4,0) rectangle (axis cs:-0.375,0.0132189786765283);
\draw[draw=none,fill=color0] (axis cs:-0.375,0) rectangle (axis cs:-0.35,0.0698717444330784);
\draw[draw=none,fill=color0] (axis cs:-0.35,0) rectangle (axis cs:-0.325,0.203477850342276);
\draw[draw=none,fill=color0] (axis cs:-0.325,0) rectangle (axis cs:-0.3,0.355023998741048);
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.275,0.514595955621997);
\draw[draw=none,fill=color0] (axis cs:-0.275,0) rectangle (axis cs:-0.25,0.712880635769923);
\draw[draw=none,fill=color0] (axis cs:-0.25,0) rectangle (axis cs:-0.225,0.916830592493502);
\draw[draw=none,fill=color0] (axis cs:-0.225,0) rectangle (axis cs:-0.2,0.952710677472651);
\draw[draw=none,fill=color0] (axis cs:-0.2,0) rectangle (axis cs:-0.175,1.1953733574632);
\draw[draw=none,fill=color0] (axis cs:-0.175,0) rectangle (axis cs:-0.15,1.3804390589346);
\draw[draw=none,fill=color0] (axis cs:-0.15,0) rectangle (axis cs:-0.125,1.52584782437642);
\draw[draw=none,fill=color0] (axis cs:-0.125,0) rectangle (axis cs:-0.1,1.59477535604688);
\draw[draw=none,fill=color0] (axis cs:-0.1,0) rectangle (axis cs:-0.075,1.7604846958848);
\draw[draw=none,fill=color0] (axis cs:-0.075,0) rectangle (axis cs:-0.05,1.91108663152097);
\draw[draw=none,fill=color0] (axis cs:-0.05,0) rectangle (axis cs:-0.025,2.09048705641672);
\draw[draw=none,fill=color0] (axis cs:-0.025,0) rectangle (axis cs:0,2.27366433236291);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.025,2.32654024706902);
\draw[draw=none,fill=color0] (axis cs:0.025,0) rectangle (axis cs:0.05,2.32811393500671);
\draw[draw=none,fill=color0] (axis cs:0.05,0) rectangle (axis cs:0.0750000000000001,2.26296325438667);
\draw[draw=none,fill=color0] (axis cs:0.0750000000000001,0) rectangle (axis cs:0.1,2.10968604925645);
\draw[draw=none,fill=color0] (axis cs:0.1,0) rectangle (axis cs:0.125,2.15437878668663);
\draw[draw=none,fill=color0] (axis cs:0.125,0) rectangle (axis cs:0.15,1.78361790856873);
\draw[draw=none,fill=color0] (axis cs:0.15,0) rectangle (axis cs:0.175,1.58785112912109);
\draw[draw=none,fill=color0] (axis cs:0.175,0) rectangle (axis cs:0.2,1.44590447714217);
\draw[draw=none,fill=color0] (axis cs:0.2,0) rectangle (axis cs:0.225,1.22086710205366);
\draw[draw=none,fill=color0] (axis cs:0.225,0) rectangle (axis cs:0.25,1.01125186875443);
\draw[draw=none,fill=color0] (axis cs:0.25,0) rectangle (axis cs:0.275,0.805413486505622);
\draw[draw=none,fill=color0] (axis cs:0.275,0) rectangle (axis cs:0.3,0.800220316311271);
\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.325,0.62758674954756);
\draw[draw=none,fill=color0] (axis cs:0.325,0) rectangle (axis cs:0.35,0.600834054606967);
\draw[draw=none,fill=color0] (axis cs:0.35,0) rectangle (axis cs:0.375,0.396254622708316);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.4,0.300574396097251);
\draw[draw=none,fill=color0] (axis cs:0.4,0) rectangle (axis cs:0.425,0.197497836179084);
\draw[draw=none,fill=color0] (axis cs:0.425,0) rectangle (axis cs:0.45,0.168384609331968);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.475,0.156581949799354);
\draw[draw=none,fill=color0] (axis cs:0.475,0) rectangle (axis cs:0.5,0.068455425289165);
\draw[draw=none,fill=color0] (axis cs:0.5,0) rectangle (axis cs:0.525,0.0550790778188679);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.55,0.066094893382642);
\draw[draw=none,fill=color0] (axis cs:0.55,0) rectangle (axis cs:0.575,0.0275395389094342);
\draw[draw=none,fill=color0] (axis cs:0.575,0) rectangle (axis cs:0.6,0.0275395389094339);

@@

0.0308218751896741 0
0.0308218751896741 3

@@

\addlegendentry{$\mu = 0.031$}

@@

-0.179871006878183 1
0.197679132295466 1

@@

\addlegendentry{$\sigma = 0.172$}

>>>>

\draw[draw=none,fill=color0] (axis cs:-0.4,0) rectangle (axis cs:-0.375,0.00551481774368941);
\draw[draw=none,fill=color0] (axis cs:-0.375,0) rectangle (axis cs:-0.35,0.0605814218347914);
\draw[draw=none,fill=color0] (axis cs:-0.35,0) rectangle (axis cs:-0.325,0.168699423699822);
\draw[draw=none,fill=color0] (axis cs:-0.325,0) rectangle (axis cs:-0.3,0.340262186728983);
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.275,0.48172967019454);
\draw[draw=none,fill=color0] (axis cs:-0.275,0) rectangle (axis cs:-0.25,0.661723210849365);
\draw[draw=none,fill=color0] (axis cs:-0.25,0) rectangle (axis cs:-0.225,0.926167683238105);
\draw[draw=none,fill=color0] (axis cs:-0.225,0) rectangle (axis cs:-0.2,1.1131441320768);
\draw[draw=none,fill=color0] (axis cs:-0.2,0) rectangle (axis cs:-0.175,1.19038558853121);
\draw[draw=none,fill=color0] (axis cs:-0.175,0) rectangle (axis cs:-0.15,1.39560413532974);
\draw[draw=none,fill=color0] (axis cs:-0.15,0) rectangle (axis cs:-0.125,1.38890799766854);
\draw[draw=none,fill=color0] (axis cs:-0.125,0) rectangle (axis cs:-0.1,1.45486223069012);
\draw[draw=none,fill=color0] (axis cs:-0.1,0) rectangle (axis cs:-0.075,1.89014334843844);
\draw[draw=none,fill=color0] (axis cs:-0.075,0) rectangle (axis cs:-0.05,1.80399178478282);
\draw[draw=none,fill=color0] (axis cs:-0.05,0) rectangle (axis cs:-0.025,2.15561058973456);
\draw[draw=none,fill=color0] (axis cs:-0.025,0) rectangle (axis cs:0,2.33061276076321);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.025,2.24024442959031);
\draw[draw=none,fill=color0] (axis cs:0.025,0) rectangle (axis cs:0.05,2.34890403251458);
\draw[draw=none,fill=color0] (axis cs:0.05,0) rectangle (axis cs:0.0750000000000001,2.31095726097247);
\draw[draw=none,fill=color0] (axis cs:0.0750000000000001,0) rectangle (axis cs:0.1,2.33900171768764);
\draw[draw=none,fill=color0] (axis cs:0.1,0) rectangle (axis cs:0.125,2.07598627244674);
\draw[draw=none,fill=color0] (axis cs:0.125,0) rectangle (axis cs:0.15,1.71987564844275);
\draw[draw=none,fill=color0] (axis cs:0.15,0) rectangle (axis cs:0.175,1.65165022964706);
\draw[draw=none,fill=color0] (axis cs:0.175,0) rectangle (axis cs:0.2,1.40256222683377);
\draw[draw=none,fill=color0] (axis cs:0.2,0) rectangle (axis cs:0.225,1.18758980571923);
\draw[draw=none,fill=color0] (axis cs:0.225,0) rectangle (axis cs:0.25,1.0980208933351);
\draw[draw=none,fill=color0] (axis cs:0.25,0) rectangle (axis cs:0.275,0.803715750920935);
\draw[draw=none,fill=color0] (axis cs:0.275,0) rectangle (axis cs:0.3,0.742179116696122);
\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.325,0.678702875114039);
\draw[draw=none,fill=color0] (axis cs:0.325,0) rectangle (axis cs:0.35,0.583516431505742);
\draw[draw=none,fill=color0] (axis cs:0.35,0) rectangle (axis cs:0.375,0.398341719580722);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.4,0.257727424376927);
\draw[draw=none,fill=color0] (axis cs:0.4,0) rectangle (axis cs:0.425,0.229546935490747);
\draw[draw=none,fill=color0] (axis cs:0.425,0) rectangle (axis cs:0.45,0.210112717761985);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.475,0.129179090828181);
\draw[draw=none,fill=color0] (axis cs:0.475,0) rectangle (axis cs:0.5,0.0899034779939157);
\draw[draw=none,fill=color0] (axis cs:0.5,0) rectangle (axis cs:0.525,0.0431810229330879);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.55,0.0479789143700981);
\draw[draw=none,fill=color0] (axis cs:0.55,0) rectangle (axis cs:0.575,0.0287873486220588);
\draw[draw=none,fill=color0] (axis cs:0.575,0) rectangle (axis cs:0.6,0.0143936743110293);

@@

0.0318388478807404 0
0.0318388478807404 3

@@

\addlegendentry{$\mu = 0.032$}

@@

-0.177435597378694 1
0.197481062716323 1

@@

\addlegendentry{$\sigma = 0.170$}
